Convergence of Forecasting Models in Climate Prediction Markets: An Agent-Based Simulation

### 2016-03-03 paper.Rmd

---
title: "Climate Prediction Markets and the Convergence of Forecasting Models: An Agent-Based Simulation"
author: " "
date: "March 1, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---

@@

library(ggplot2)
library(pander)
```

@@

We present an agent-based simulation model of a climate prediction market. Traders adapt their beliefs about the future global temperatures based on the monetary performance of their neighboring traders in a social network. We conduct simulation experiments with the model to determine how a variety of market factors and the climate data-generating process affect whether climate prediction markets foster a convergence of market participants' beliefs regarding a true model of the global climate.

@@

The climate change debate has become strongly polarized over the past twenty years. Although the scientific consensus on the anthropogenic nature of climate change strongly increased, the average belief about anthropogenic climate change did not evolve much within the public [@Vandenbergh2013f]. In addition, the divide on anthropogenic climate change between liberals and conservatives has grown steadily as the question is becoming increasingly politicized and potentially disconnected from scientific evidence. The costs of misinformed climate policies are high. If anthropogenic climate change is a myth but is taken to be true, public resources will be spent on unnecessary efforts. On the other hand, if climate change is human-induced but not recognized as so, the costs of inaction could be devastating. Given that effective climate policies require long-lasting measures to be taken, the importance of an accurate consensus on the issue is manifest.

@@

```{r sa, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("sa", "Sensitivty analysis"), fig.width=5, fig.height=5}
library(eat)
load("output/src_future.Rda")
plot(src_future, outcome_var = "Convergence") + theme_classic() 
#multi_plot(p1, p2, cols = 2)
```

>>>>

---
title: "Convergence of Forecasting Models in Climate Prediction Markets: An Agent-Based Simulation"
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "March 2, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---

@@

library(ggplot2)
theme_set(theme_classic())
library(pander)
```

@@

We present an agent-based simulation of a climate prediction market. Traders adapt their beliefs about the future global temperatures based on the monetary performance of their neighboring traders in a social network. We conduct simulation experiments with the model to determine how a variety of market factors and the climate data-generating process affect whether climate prediction markets foster a convergence of market participants' beliefs regarding a true model of the global climate.

@@

The climate change debate has become strongly polarized over the past twenty years. Although the scientific consensus on the anthropogenic nature of climate change strongly increased, beliefs about anthropogenic climate change did not evolve much within the public [@Vandenbergh2013f]. In addition, the divide on anthropogenic climate change between liberals and conservatives has grown steadily as the question is becoming increasingly politicized and potentially disconnected from scientific evidence. The costs of misinformed climate policies are high. If anthropogenic climate change is a myth but is taken to be true, public resources will be spent on unnecessary efforts. On the other hand, if climate change is human-induced but not recognized as so, the costs of inaction could be devastating. Given that effective climate policies require long-lasting measures to be taken, the importance of an accurate consensus on the issue is manifest.

@@

```{r sa, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("sa", "Estimated Effects on Convergence of Beliefs in Future Scenario "), fig.width=4, fig.height=4.5}
# library(eat)
# load("output/src_future.Rda")
# plot(src_future, outcome_var = "Convergence") + theme_classic() + theme(text=element_text(family='Palatino'))

source("utils/sa_plot.R")
sa_plot() + theme(text=element_text(family='Palatino'))
#multi_plot(p1, p2, cols = 2)
```

```{r time, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("time", "Time"), fig.width=5, fig.height=10}
source("utils/time_plot.R")
time_plot() + theme(text=element_text(family='Palatino'))
```
